---
title: "Sentiment Analysis on Yelp Reviews of Indian Restaurants in New York"
author: "Deepti Gupta, Shashank Tiwari, Bhargavi Gutta"
date: "2/25/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Objective
The entrepreneurs in the restaurant business can use reviews provided by their users in order to unlock the hidden value of text to understand their customers’ opinions and needs and make better, more informed, business decisions. This study is an analysis of the Yelp Reviews provided by Yelp fusion business API of Indian restaurants in New York study. This study will let us harness the power of analytics and Natural Language Processing to extract meaning from text and dive into opinions of customers and see them outside of the often-controlled environment of a survey. The analysis will include sentiment analysis using label classification and word cloud formation capturing the most important words used in the Indian food community.


# Method and Data Variables
The participants in this study are the 50 food businesses across the New York City County (Manhattan, NY) whose business data was extracted from an API request made to Yelp Fusion. The sample was retrieved by searching "Indian Food" tag which returned top 50 records per API request and is a convenience sample. The criteria specified under the request is first the business vendor should be a licensed food business, situated with in the county of New York City, i.e. Manhattan, New York, NY and business entry should exist under Yelp. The first request is using Business Search API which returned the Business Ids which was used further to request the second API - User Reviews which returned the top 3 reviews. Following are the set of columns combined from both the APIs to be used under this study. BusinessName - is the official name of the business, BusinessRating - is the overall business rating on yelp, Name - is the user name who provided the review, UserRating - is the rating provided by the respective user, and lastly and most importantly, UserReview - user review text provided by the user. Total observations in this study are 150, consisting of 50 unique businesses with 3 reviews of each of it.


```{r}
library(reticulate)
```

```{python}
#py_install("yelp", pip = T) 
#py_install("yelpapi", pip = T) 

import yelpapi  
import argparse

import json
import http.client
import urllib.parse
from yelp.client import Client

import spacy
nlp = spacy.load("C:\Program Files\Python38\Lib\site-packages\en_core_web_sm\en_core_web_sm-2.2.0")

import pandas as pd
import nltk

from __future__ import print_function
import requests

import unicodedata   # Used for processing raw texts

import contractions  # Used to remove contractions
import re
from contractions import contractions_dict

from nltk.corpus import stopwords

from textblob import Word
from textblob import TextBlob

```

# Section 1. Load the Data
## Get Business IDs and user reviews for these business ids.
```{python}
#
#CLIENT_KEY = "mkiXAI4ESi8xsGpizf7u0g"
#MY_API_KEY = "zUHqRv5saa5CrIhddvDahzEsETysJgFkmyESbYzopq_Zh7Ca5wvtUyYWilD91h_Ff0WkownQoP4oz4z1KwwVPfnrtleB6ZvMPq_fbVYRPJBK_HZS0nlnIej#QEP5bXnYx"
# 
#business_url='https://api.yelp.com/v3/businesses/search'
#
#headers = {
#        'Authorization': 'Bearer {}'.format(MY_API_KEY),
#    }
#
#def yelp_search(term): # This function launches the request for all grocery location endpoints 
#    url_params = { 
#        'term':term,'location':'New York City','limit':50
#     }
#
#    response = requests.get(business_url, headers=headers, params=url_params)
#    return response.json() 
#
#output_json1 = yelp_search('Indian Food') 
#
#df_first1 = pd.DataFrame.from_dict(output_json1['businesses'])
#
#businesses = output_json1["businesses"]
#
#cols = ['BusinessName',"BusinessRating",'UserName',"UserRating","UserReview"]
#lst = []
#
#for business in businesses:
#    id = business["id"]
#    url="https://api.yelp.com/v3/businesses/" + id + "/reviews"
#    response = requests.get(url, headers=headers)
# 
#    output = json.loads(response.text)
# 
#    reviews = output["reviews"]
#    for review in reviews:
#       lst.append((business["name"],business["rating"], review["user"]["name"], review["rating"], review["text"]))
#   
#bus_review_sub1 = pd.DataFrame(lst,columns=cols)
#
#bus_review_sub1.to_csv("C:\\Study\\520-NaturalLanguageProcessing\\Project\\data\\business_reviews.csv", index = False )        
    
```

## Section2. Checkpoint file
```{python}

bus_review_sub2 = pd.read_csv("C:\\Study\\520-NaturalLanguageProcessing\\Project\\data\\business_reviews.csv")
bus_review_sub2   
```

## Section3. Processing raw text
### 3.1 Remove special symbols
```{python}
#---------------------------------------------------------------------------------
# Using the library - `unicodedata` in python to remove any symbols from your text

# Will convert to lowercase after contractions since keys in contractions can have upper case letters like I've


def remove_accented_chars(text):
  text = unicodedata.normalize('NFKD', text).encode('ascii', 'ignore').decode('utf-8', 'ignore')
  return text

bus_review_sub2['No_Symbols'] = bus_review_sub2.UserReview.apply(lambda x: remove_accented_chars(x))

```


### 3.2 Apply Contractions
```{python}

#Modify month keys in contraction_dict since they are throwing errors with .(fullstop)
if contractions_dict.get("jan.") != None:
	contractions_dict['jan'] = contractions_dict.pop('jan.')

if contractions_dict.get("feb.") != None:	
	contractions_dict['feb'] = contractions_dict.pop('feb.')
	
if contractions_dict.get("mar.") != None:	
	contractions_dict['mar'] = contractions_dict.pop('mar.')

if contractions_dict.get("apr.") != None:	
	contractions_dict['apr'] = contractions_dict.pop('apr.')
													
if contractions_dict.get("jun.") != None:					
	contractions_dict['jun'] = contractions_dict.pop('jun.')

if contractions_dict.get("jul.") != None:
	contractions_dict['jul'] = contractions_dict.pop('jul.')

if contractions_dict.get("aug.") != None:
	contractions_dict['aug'] = contractions_dict.pop('aug.')
													
if contractions_dict.get("sep.") != None:													
	contractions_dict['sep'] = contractions_dict.pop('sep.')

if contractions_dict.get("oct.") != None:	
	contractions_dict['oct'] = contractions_dict.pop('oct.')

if contractions_dict.get("nov.") != None:	
	contractions_dict['nov'] = contractions_dict.pop('nov.')

if contractions_dict.get("dec.") != None:	
	contractions_dict['dec'] = contractions_dict.pop('dec.')

contractions_re = re.compile('|'.join(contractions_dict.keys()))

def expand_contractions(s, contractions_dict=contractions_dict):
  def replace(match):
    return contractions_dict[match.group(0)]
  return contractions_re.sub(replace, s)


bus_review_sub2['No_Contractions'] = bus_review_sub2.No_Symbols.apply(lambda x: expand_contractions(x))


```

### 3.3 Correct Misspellings
```{python}

Spelling_Corrected = []

for line in bus_review_sub2.No_Contractions:
    text = TextBlob(line).correct()
    Spelling_Corrected.append(str(text))
    
bus_review_sub2["Spelling"] = Spelling_Corrected 

```


### 3.4 Lemmetization
```{r}
library(textstem)

py$bus_review_sub2$Lemmatized = lemmatize_strings(py$bus_review_sub2$Spelling)

```

### 3.5 Remove Stopwords
```{python}
stop = stopwords.words('english')

bus_review_sub2['No_Stop_Words'] = bus_review_sub2['Lemmatized'].apply(lambda x: ' '.join([word for word in x.split() if word not in (stop)]))
stop
```

### 3.6 Convert to lowercase
```{python}

bus_review_sub2['Lower_Case'] = bus_review_sub2.No_Stop_Words.str.lower()

```



```{r}

#View(py$bus_review_sub2)
head(py$bus_review_sub2)

```